When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-12-04 code/Submissionv4.Rmd
commit

summary(mod4)
tidy(mod4)
glance(mod4)
```

```{r regression table, include=TRUE, echo=FALSE, results="asis"}
stargazer(mod3, mod4, 
          title="Table 3: Logistic Regression Results", 
          column.labels = c('Legislative Activity, Criticize, or Partisan','Criticize or Partisan'),
          covariate.labels = c('Institutional Credibility', 'Congressional Polarization', 'Male', 'Mixed Authorship', 'Unknown Authorship', 'Rank'),
          align=TRUE)

>>>>

summary(mod4)
tidy(mod4)
glance(mod4)

#model 5 - now check for robustness using aff_polar as the polarization variable
mod5 <- glm(leg_crit_part ~ Inst_Cred_Gallup + aff_polar + AuthSex + AuthRank,
    family=binomial(link="logit"),
    data=polaradjdataset
    )

summary(mod5)

mod6 <- glm(crit_part ~ Inst_Cred_Gallup + aff_polar + AuthSex + AuthRank,
    family=binomial(link="logit"),
    data=polaradjdataset
    )

summary(mod6)
```

```{r regression table, include=TRUE, echo=FALSE, results="asis"}
stargazer(mod3, mod4, mod5, mod6,
          title="Table 3: Logistic Regression Results", 
          column.labels = c('Model 3','Model 4','Model 5', 'Model 6'),
          covariate.labels = c('Institutional Credibility', 'Congressional Polarization', 'Affective Polarization', 'Male', 'Mixed Authorship', 'Unknown Authorship', 'Rank'),
          align=TRUE)
